\chapter{Personal evaluation of the practicum }

	My mentor, Manuel Rego guided me through the application design and coding, he taught me how JQueryMobile, PhoneGap works, and how to go 
	step-by-step. Also I have reused several SergasApp functions from Manuel's application. 
	
Firstly, it was really difficult to prepare environment, because there a lot of incompatibilities among plug-ins, Eclipse versions and so on.
Eventually I find out an uptodate version (Juno) which works with Aptana Plugins, Android SDK, even Git control versions. As well I found the correct version of each library. 

	On the other hand, in the beginning write code was not so complicated, despite of application work-flow confusion and increasing complexity. 	
	These complexity were decreasing as far as I used one function to do only one task and I did not need to add more global variables.
To avoid that complexity I have to rewrite several functions.

	Honestly, I believed that I was not a good coder, nor a good graphical user interface designer neither a good database designer; but
	at this point I realized how important is to simplify objects (windows, functions, ...) as much as possible, and reuse ideas from one point to another. And, 
	is very important to study and learn from others applications (interface and code). Also I realized that Siestta developer did a good job. 
	
	Eventually, I have learnt several technologies (Android, WebSQL, git, etc) and I have done my first Android App, I am confident that soon I will use 
this application in my daily work.
