\chapter{Results}

Application is evolving from list, edit students and groups, to its final goals. These objectives were fulfilled:
\section{Objectives completed}
\begin{itemize}
  \item Access to any workday, any group and student.
  \item Management of attendance and misbehaviour of each student. The students information is still hard-coded into source files.
  \item 
\end{itemize}

\section{Technical details}


\section{Further objectives}

\begin{itemize}
\item Links to student and group management. These pages were done but links are not missing into main application window.
\item There are several objectives not fulfilled yet, but I am on the way to get those done, those are, in priority order:
\item Data visualization. Student attendance and misbehaviour have to be shown in table-like window.
\item Test into real hardware. EduXes.apk has to be copied into mobile phone.
\item Activities evaluation per student. A window to display activities marks and final mark.
\item Timetable management. A window to manage groups timetable. When a group has class with this teacher.
\item Server synchronization with a custom application or



\end{itemize}

These objectives were not fulfilled because time and skills lack.



En este apartado deberán quedar reflejados los experimentos
realizados. Para ello se mostrarán:




\section {Resultados en forma de tablas, gráficas e imágenes donde se describa cuantitativa
            y cualitativamente el funcionamiento de la aplicación} \dots

\section {Análisis crítico de los resultados con el objetivo de decidir si el sistema implementado es válido}
\dots
\begin{verbatim}
 ohcount -i  assets/www/js/database.js assets/www/js/interface.js \
 assets/www/js/create_populate_db.js  assets/www/index.html \
 assets/www/remove.html 
Examining 5 file(s)
                              Ohloh Line Count                              
Language               Code    Comment  Comment %      Blank      Total  File
----------------  ---------  ---------  ---------  ---------  ---------  -----------------------------------------------
javascript             1374        155      10.1%        210       1739  database.js
javascript              393         91      18.8%         56        540  interface.js
javascript              402         57      12.4%         46        505  create_populate_db.js
html                    546         99      15.3%        117        762  index.html
javascript                1          0       0.0%          0          1  index.html
html                     28          1       3.4%          8         37  remove.html

\end{verbatim}
