\chapter{Description of the practicum}
%\thispagestyle {empty}
The main objective of this Master Thesis consist in the development of an mobile application to be used int highschools by teachers.
It could allows teachers to carry on control students attendance, their behavior. Also it permits quick assessment by activity.
Teachers would read students reports: weekly and daily assessment, by activity assessments and total marks.
\begin{itemize}
  \item {Name :} Jos\'e Antonio Salgueiro Aquino.
  \item {Birth date: } august 5th 1970
\item {Education:} B.Sc. in Fundamental Physics, University of Santiago de Compostela University 1988-1993.
\item {Address:} Marin (Pontevedra). Spain.
\item {Current position: } Secondary School teacher in Technology.
\end{itemize}

Working times (planned) :
  300 hours. 	From 6th August, to 30 September, on an eight hours day basis.

Technologies involved:
\begin{itemize}
  \item  Java \texttrademark  language.
  \item  Android \texttrademark  . The operatig  skeleton application.
  \item  PhoneGap \texttrademark (alias Cordova ) framework to develop multi-platform applications.
  \item  JQuery and JqueryMobile to development of mobile oriented applications.
  \item  JavaScript with Web Databases.
  \item  Git for version control system.
  \item \LaTeX{} for documentation.
\end{itemize}

Meetings:
\begin{itemize}
  \item Technologies to be used were stated, work methodologies, first application windows (pages), Android version to be used (2.3.3) because is the most popular. 
  \item	Several emails and gtalk conversations about organization, general problems were written.
\end{itemize}
Teleworking is carried on 


Materials and special equipment used:
\begin{itemize}
  \item {Hardware: } Intel Quad, 6GiB RAM, 500GiB HD. 
  \item {Software: } Debian GNU/Linux Wheezy (testing), Eclipse Juno, JQuery 1.8.1, jQueryMobile 1.1.1, and PhoneGap-Cordova 1.8.1, Android Virtual Manager 2.3.3, Git 1.7.10.4-1.
\item { Real testing: } Sony-Ericsson Xperia V mobile phone, with USB cable and wifi.
\end{itemize}

    
    
